Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-08-24 doc/main_jfm.tex
re-calculated table 1

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{Slip.eps}
\includegraphics[width=0.4\textwidth]{Slip2.eps}
\end{center} 
  \caption{The schematic of the intermonolayer slip over a period of time. Taking shear rate $\chi=0.005$ as an example, we denote the mean angle between each particle pair $\theta(t)$ where the angle is calculated from the relative position of particles using the vesicle center of mass position. The configuration plots have two fixed particles marked in yellow and blue and labeled with the corresponding time $t=2000$ and $t=9000$. The midplane curve is denoted as $\Sigma_M$. We provide numerical results of $\theta(t)$ for cases of shear rates.
  }
    \label{figure5}
\end{figure}

@@

Table~\ref{table1} provides dimensional friction coefficients $b$ for several shear rates
and the results are in quantitative agreement with 
values previously reported in the literature~\cite{sch-vla-mik2010} and~\cite{denOtter2007}.  
The coefficients generally lie within the range 1 to 2 pN$\cdot$ns nm$^{-2}$ but there are some 
outliers.  These outliers ($\dot\gamma = 0.0041$ ns$^{-1}$ and 
$\dot\gamma = 0.0066$ ns$^{-1}$) correspond to slip velocities that are too low relative to shear rate (see the green and red curve in Figure \ref{figure5}: panel (c)).
The JP vesicle consists of only  58 particles and so it is not surprising that discrete effects produce outliers.

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{Slip.eps}
\includegraphics[width=0.4\textwidth]{Slip2.eps}
\end{center} 
  \caption{The schematic of the intermonolayer slip over a period of time. Taking shear rate $\chi=0.005$ as an example, we denote the mean angle between each particle pair $\theta(t)$ where the angle is calculated from the relative position of particles using the vesicle center of mass position. The configuration plots have two fixed particles marked in yellow and blue and labeled with the corresponding time $t=2000$ and $t=9000$. The midplane curve is denoted as $\Sigma_M$. We provide numerical results of $\theta(t)$ for cases of shear rates $\chi$.
  }
    \label{figure5}
\end{figure}

@@

Table~\ref{table1} provides dimensional friction coefficients $b$ for several shear rates
and the results are in quantitative agreement with 
values previously reported in the literature~\cite{sch-vla-mik2010} and~\cite{denOtter2007}.  
The coefficients generally lie within the range 0.2 to 0.3 pN$\cdot$ns nm$^{-3}$ but there are some 
outliers.  These outliers ($\dot\gamma = 0.0041$ ns$^{-1}$ and 
$\dot\gamma = 0.0066$ ns$^{-1}$) correspond to slip velocities that are too low relative to shear rate (see the green and red curve in Figure \ref{figure5}: panel (c)).
The JP vesicle consists of only  58 particles and so it is not surprising that discrete effects produce outliers.
